---
title: "Figures for architecture_of_multiattribute_choice paper"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    theme: paper
    highlight: pygments
    df_print: kable
---


# Veridical Numeric Task

Before creating our plots we need to load in packages and prepare some convenience functions and themes for plotting.

## Load Packages

I use the tidyverse a lot, so we'll load that all in now, we also need the `BayesFactor` package, and `ggpubr` for combining subplots into larger figures. We'll also tell knitr to create all figures at the full column width.

```{r, message = FALSE}
library(dplyr)
library(ggplot2)
library(ggh4x)
library(stringr)
library(patchwork)
library(watercolours)
library(mcce)   # devtools::install_github('gjcooper/gcphd-model_of_dce')
knitr::opts_chunk$set(out.width = "100%")
```

## Load Data

```{r read_data}
# Load all the samples
accept_file <- here::here("data", "output", "NumericVDCE_1878182.rcgbcm_Estimation5Model.RData")
reject_file <- here::here("data", "output", "NumericVDCE_2117450.rcgbcm_RejectEstimation5Model.RData")

samples <- list(accept = get_samples(accept_file) %>% extract_parameters(filter = "sample"),
                reject = get_samples(reject_file) %>% extract_parameters(filter = "sample")) %>%
  bind_rows(.id = "condition")

#Map of old parameter names to new ones
par_label_short <- c("ASRS", "ASRC", "ACRS", "ACRC", "Comp")
par_label_long <- c("Accept Selective Reject Selective",
                    "Accept Selective Reject Complete",
                    "Accept Complete Reject Selective",
                    "Accept Complete Reject Complete",
                    "Compensatory")

names(par_label_short) <- c("FPP", "IST", "IEX", "MW", "CB")
names(par_label_long) <- c("FPP", "IST", "IEX", "MW", "CB")
arch_order <- c("FPP", "IST", "IEX", "MW", "CB")


```

## Plot theme

To keep things as consistent as possible we'll create a theme and update the default ggplot theme with it.

```{r}
txt_base_sz <- 12
plot_theme <- theme(
  strip.background = element_blank(),
  strip.text = element_text(face = "bold", size = txt_base_sz + 2),
  strip.placement = "outside",
  legend.title =  element_blank(),
  legend.position = "bottom",
  legend.margin = margin(0, 0, 0, 0, "cm"),
  axis.text = element_text(face = "bold", size = txt_base_sz - 2),
  axis.title = element_text(face = "bold", size = txt_base_sz + 2),
  plot.margin = margin(l = 2, r = 2, t = 2),
  plot.title = element_text(face = "bold", size = txt_base_sz + 2, hjust = 0.5),
)

bigger_text <- theme(
  axis.title = element_text(size = txt_base_sz + 4),
  strip.text = element_text(face = "bold", size = txt_base_sz + 4),
  plot.title = element_text(face = "bold", size = txt_base_sz + 4))


theme_set(theme_classic() + plot_theme)
```

## Selective Influence test

```{r}
model_medians <- samples %>%
  filter(startsWith(parameter, "alpha_"), stageid == "sample") %>%
  mutate(value = exp(value)) %>%
  group_by(subjectid, parameter) %>%
  summarise(value = median(value), condition = first(condition)) %>%
  arch_medians

Par_order <- c("IST", "CB", "FPP", "MW", "IEX")

acc_plot <- model_medians %>%
  filter(condition == "accept") %>%
  mutate(parameter = factor(parameter, levels = Par_order,
                            labels = par_label_long[Par_order])) %>%
  arch_plot +
  scale_fill_watercolour(palette = "durer") +
  theme(legend.position = "none") +
  labs(title = "Accept condition")

rej_plot <- model_medians %>%
  filter(condition == "reject") %>%
  mutate(parameter = factor(parameter, levels = Par_order,
                            labels = par_label_long[Par_order])) %>%
  arch_plot +
  scale_fill_watercolour(palette = "durer") +
  theme(legend.position = "right",
        legend.key.size = unit(2, "cm")) +
  labs(title = "Reject condition")

layout <- "
AAAAAAAAA
BBBB##CC#
"
acc_plot + rej_plot + guide_area() +
  plot_layout(design = layout, guides = "collect")

ggsave(
  filename = here::here(
    "results",
    "arch_mac_figures",
    "salience_manipulation.png"),
  dpi = 600,
  width = 45,
  height = 30,
  units = "cm"
)
```

## Parameter values for Veridical task

```{r}
par_medians <- samples %>%
  filter(!startsWith(parameter, "alpha_"), stageid == "sample") %>%
  mutate(value = exp(value)) %>%
  group_by(subjectid, parameter) %>%
  summarise(value = median(value), condition = first(condition))

par_colours <- c("t0" = "grey",
                 "A" = "grey", "b_acc" = "#73842E", "b_rej" = "#D0781C",
                 "v_acc_p_H" = "#569F72", "v_acc_p_L" = "#407755", "v_acc_p_D" = "#2B5039",
                 "v_rej_p_H" = "#F29F40", "v_rej_p_L" = "#EF8C1A", "v_rej_p_D" = "#BF6C0D",
                 "v_acc_r_H" = "#85C0FF", "v_acc_r_L" = "#47A0FF", "v_acc_r_D" = "#0A81FF",
                 "v_rej_r_H" = "#BBA9A0", "v_rej_r_L" = "#A2887C", "v_rej_r_D" = "#83685D")

par_medians %>%
  mutate(colour = par_colours[parameter]) %>%
  ggplot(aes(x = parameter, y = value, fill = colour)) +
  scale_colour_watercolour(palette = "durer") +
  scale_fill_identity() +
  geom_boxplot() +
  coord_flip() +
  facet_wrap(~ condition)

ggsave(
  filename = here::here(
    "results",
    "arch_mac_figures",
    "vnumeric_pars.png"),
  dpi = 600,
  width = 45,
  height = 30,
  units = "cm"
)
```

# Simulation

## Prep for data reads and get original data

```{r}
# Load all the samples
data_location <- here::here("data", "output", "VeridicalRecovery")
odata <- "NumericVDCE_1878182.rcgbcm_Estimation5Model.RData"

recovery_files <- list.files(data_location, pattern = ".RData")
recovery_data_files <- list.files(data_location, pattern = ".RDS")

original_samples <- get_samples(here::here("data", "output", odata))
```

## Read in generated data

```{r}
recovery_data <- lapply(recovery_data_files, function(x) {
  print(paste("Reading data", x))
  readRDS(here::here(data_location, x))
})
names(recovery_data) <- sapply(strsplit(recovery_data_files, "_"), "[[", 2)

recovery_data[["Original"]] <- original_samples$data %>%
  mutate(generator = "participant")
recovery_data <- bind_rows(recovery_data, .id = "source")
```

## Data plots

### Plot 1

```{r}
recovery_data %>%
  filter(rt < 10) %>%
  mutate(accept = factor(accept, labels = c("Reject", "Accept"))) %>%
  ggplot(aes(x = source, y = rt, colour = generator)) +
  geom_boxplot() +
  facet_wrap(~ accept) +
  scale_colour_watercolour(palette = "durer")

```

### Plot 2

```{r}
recovery_data %>%
  filter(rt < 5) %>%
  mutate(simulated = ifelse(source == "Original", "No", "Yes")) %>%
  mutate(cell=paste0(price, rating)) %>%
  ggplot(aes(x = rt, colour = source, linetype=simulated)) +
  geom_density(linewidth=0.7) +
  scale_colour_watercolour(palette = "durer") +
  facet_wrap(~ cell)
```


## Read in the samples

```{r}
samples <- lapply(recovery_files, function(x) {
  print(paste("Extracting", x))
  get_samples(here::here(data_location, x)) %>%
    extract_parameters(filter = "sample")
})
names(samples) <- sapply(strsplit(recovery_files, "_"), "[[", 2)

samples[["Original"]] <- original_samples %>% extract_parameters(filter = "sample")

samples <- bind_rows(samples, .id = "source")
rm(original_samples)

```

## Get Architecture Medians

```{r}
model_medians <- samples %>%
  filter(startsWith(parameter, "alpha_"), stageid == "sample") %>%
  mutate(value = exp(value)) %>%
  group_by(source, subjectid, parameter) %>%
  summarise(value = median(value)) %>%
  arch_medians(grouping_vars = c("source", "subjectid"))
```

## Get subject order for plot

```{r}
subject_order <- model_medians %>%
  filter(subjectid != "Group") %>%
  group_by(subjectid, source) %>%
  summarise(maxRel = max(rel_val)) %>%
  group_by(subjectid) %>%
  summarise(meanMax = mean(maxRel)) %>%
  arrange(desc(meanMax)) %>%
  pull(subjectid)
```

## Get parameter order

```{r}
Par_order <- model_medians %>%
  filter(source == "Original") %>%
  group_by(parameter) %>%
  summarise(median_val = median(rel_val)) %>%
  arrange(median_val) %>%
  pull(parameter)
```

## Architecture recovery

```{r}
subject_recovery <- model_medians %>%
  filter(source != "Original") %>%
  filter(subjectid != "Group") %>%
  mutate(subjectid = factor(subjectid, subject_order)) %>%
  mutate(parameter = factor(parameter, Par_order,
                            labels = par_label_long[Par_order])) %>%
  mutate(source = factor(source, Par_order,
                         labels = par_label_long[Par_order])) %>%
  ggplot(aes(x = subjectid, y = rel_val, fill = parameter)) +
    geom_col() +
    labs(y = "Relative Evidence") +
    scale_fill_watercolour(palette = "durer") +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          strip.background = element_blank(),
          strip.text.y = element_blank()) +
    facet_grid(rows = vars(source)) +
    scale_y_continuous(labels = NULL, breaks = NULL) +
    ggtitle("Indidividual Subjects")

group_recovery <- model_medians %>%
  filter(source != "Original") %>%
  filter(subjectid == "Group") %>%
  mutate(subjectid = factor(subjectid, subject_order)) %>%
  mutate(parameter = factor(parameter, Par_order,
                            labels = par_label_long[Par_order])) %>%
  mutate(source = factor(source, Par_order,
                         labels = par_label_long[Par_order])) %>%
  ggplot(aes(x = subjectid, y = rel_val, fill = parameter)) +
    geom_col() +
    scale_fill_watercolour(palette = "durer") +
    theme(axis.title = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank()) +
    facet_grid(rows = vars(source)) +
    scale_y_continuous(labels = NULL, breaks = NULL) +
    ggtitle("Group Level")

subject_recovery + group_recovery +
  plot_layout(widths = c(6, 1), guides = "collect") +
  plot_annotation(
    title = "Relative Evidence for each of the 5 architectures",
    subtitle = "Each row corresponds to the generating architecture",
    caption = "The area of each stacked bar is the relative proportion of each of the five possible modelled architectures as their dirichlet process"
    )

ggsave(
  filename = here::here(
    "results",
    "arch_mac_figures",
    "simulation_recovery.png"),
  dpi = 600,
  width = 45,
  height = 30,
  units = "cm"
)
```

## Parameter Recovery

```{r}
par_medians <- samples %>%
  filter(!startsWith(parameter, "alpha_")) %>%
  group_by(source, subjectid, parameter) %>%
  summarise(value = median(value))

recovery <- par_medians %>% filter(source != "Original")
original <- par_medians %>% filter(source == "Original")

combined <- recovery %>%
  left_join(original, by = c("parameter", "subjectid")) %>%
  select(-source.y) %>%
  rename(
    recovered_value = value.x,
    estimated_value = value.y,
    recovery_model = source.x
  ) %>%
  mutate(recovery_model = factor(recovery_model, levels = arch_order,
                                 labels = par_label_short[arch_order])) %>%
  mutate(subjectid = case_when(
    subjectid == "theta_mu" ~ "Group",
    TRUE ~ str_pad(subjectid, 2, pad = "0")
  ))

pt_col <- watercolour$durer$discrete["shadow"]

parplot <- function(subset) {
  subset %>%
  ggplot(aes(x = estimated_value, y = recovered_value)) +
  geom_point(size = 0.5, colour = pt_col) +
  geom_abline(intercept = 0, slope = 1) +
  facet_grid2(rows = vars(parameter),
              cols = vars(recovery_model),
              scales = "free",
              independent = "x") +
  labs(
    x = "Generating Value",
    y = "Recovered Value"
  )
}

pars <- c("A", "t0", "b_acc", "b_rej")
plabs <- c("Start Point", "Non-decision Time",
           "Threshold to Accept", "Threshold to Reject")
combined %>%
  filter(parameter %in% pars) %>%
  mutate(parameter = factor(parameter, levels = pars, labels = plabs)) %>%
  parplot()

ggsave(
  filename = here::here(
    "results",
    "arch_mac_figures",
    "parameter_recovery_other.png"),
  dpi = 600,
  width = 45,
  height = 30,
  units = "cm"
)

```

### Accept drift rates

```{r}
acc_dr <- c("v_acc_p_D", "v_acc_r_D",
            "v_acc_p_L", "v_acc_r_L",
            "v_acc_p_H", "v_acc_r_H")
drlabs <- c("Price Distractor", "Rating Distractor",
            "Price Low", "Rating Low",
            "Price High", "Rating High")
combined %>%
  filter(startsWith(parameter, "v_acc")) %>%
  mutate(parameter = factor(parameter, levels = acc_dr, labels = drlabs)) %>%
  parplot

ggsave(
  filename = here::here(
    "results",
    "arch_mac_figures",
    "parameter_recovery_drift_acc.png"),
  dpi = 600,
  width = 45,
  height = 30,
  units = "cm"
)
```

### Reject drift rates

```{r}
rej_dr <- c("v_rej_p_D", "v_rej_r_D",
            "v_rej_p_L", "v_rej_r_L",
            "v_rej_p_H", "v_rej_r_H")
drlabs <- c("Price Distractor", "Rating Distractor",
            "Price Low", "Rating Low",
            "Price High", "Rating High")

combined %>%
  filter(startsWith(parameter, "v_rej")) %>%
  mutate(parameter = factor(parameter, levels = rej_dr, labels = drlabs)) %>%
  parplot

ggsave(
  filename = here::here(
    "results",
    "arch_mac_figures",
    "parameter_recovery_drift_rej.png"),
  dpi = 600,
  width = 45,
  height = 30,
  units = "cm"
)
```

# Architecture Explainer

```{r}
one_acc_plot <- function(racecol = "darkgreen", diagcol = "black", end = c(0.8, 0.8), width = 1) {
  ggplot(data.frame(x = seq(0, 1, 0.1), y = seq(0, 1, 0.1)),
         aes(x = x, y = y)) +
  geom_blank() +
  geom_hline(yintercept = 0.9, linetype = 2, colour = diagcol) +
  geom_segment(
    x = 0, y = 0,
    xend = end[1], yend = end[2],
    lineend = "round", # See available arrow types in example above
    linejoin = "mitre",
    linetype = 1,
    linewidth = width,
    arrow = arrow(length = unit(0.3, "inches")),
    colour = racecol # Also accepts "red", "blue' etc
  ) +
  theme_void() +
  theme(
    axis.line = element_line(linewidth=width, colour = diagcol),
    axis.title = element_blank(),
    axis.text = element_blank()
  ) +
  scale_x_continuous(expand = c(0, 0), limits = c(0, 1)) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 1))
}
```

```{r arch_specific_plots}
plot_canvas <- function(xmax = 1, ymax = 1) {
  ggplot(data.frame(x = seq(0, xmax, length.out = 10), y = seq(0, ymax, length.out = 10)),
         aes(x = x, y = y)) +
    geom_blank() +
    scale_x_continuous(expand = c(0, 0), limits = c(0, xmax)) +
    scale_y_continuous(expand = c(0, 0), limits = c(0, ymax)) +
    theme_void() +
    theme(panel.background = element_rect(fill = "white", colour = "black"))

}

arch_schema_plot <- function(arch) {
  p <- plot_canvas() +
    theme(
      plot.title = element_text(size = 24, hjust = 0.5)
    ) +
    coord_fixed()

  arch_spec <- arch_schema[[arch]]
  for (component in arch_spec$components) {
    lba <- do.call(one_acc_plot, component$args)
    annote_args <- c(list(grob = ggplotGrob(lba)), component$pos)
    p <- p + do.call(annotation_custom, annote_args)
  }
  p + ggtitle(arch_spec$name)
}

greengrey <- "#C5D3C5"
redgrey <- "#D3C5C5"

arch_order <- c("FPP", "IST", "IEX", "MW", "CB")
arch_schema <- list(
  ASRS = list(name = "Accept Selective Reject Selective",
              components = list(list(pos = list(xmin = 0.05, xmax = 0.45, ymin = 0.55, ymax = 0.95),
                                     args = list(racecol = "darkgreen", end = c(0.6, 0.9), width = 2)),
                                list(pos = list(xmin = 0.55, xmax = 0.95, ymin = 0.55, ymax = 0.95),
                                     args = list(racecol = redgrey, end = c(0.95, 0.8))),
                                list(pos = list(xmin = 0.05, xmax = 0.45, ymin = 0.05, ymax = 0.45),
                                     args = list(racecol = greengrey, end = c(0.7, 0.8))),
                                list(pos = list(xmin = 0.55, xmax = 0.95, ymin = 0.05, ymax = 0.45),
                                     args = list(racecol = redgrey, end = c(0.99, 0.75))))),
  ASRC = list(name = "Accept Selective Reject Complete",
              components = list(list(pos = list(xmin = 0.05, xmax = 0.45, ymin = 0.55, ymax = 0.95),
                                     args = list(racecol = "lightgrey", end = c(0.6, 0.75))),
                                list(pos = list(xmin = 0.55, xmax = 0.95, ymin = 0.55, ymax = 0.95),
                                     args = list(racecol = "darkred", end = c(0.55, 0.9), width = 2)),
                                list(pos = list(xmin = 0.05, xmax = 0.45, ymin = 0.05, ymax = 0.45),
                                     args = list(racecol = "darkgreen", end = c(0.6, 0.9), width = 2)),
                                list(pos = list(xmin = 0.55, xmax = 0.95, ymin = 0.05, ymax = 0.45),
                                     args = list(racecol = "lightgrey", end = c(0.65, 0.85))))),
  ACRS = list(name = "Accept Complete Reject Selective",
              components = list(list(pos = list(xmin = 0.05, xmax = 0.45, ymin = 0.55, ymax = 0.95),
                                     args = list(racecol = "darkgreen", end = c(0.6, 0.9), width = 2)),
                                list(pos = list(xmin = 0.55, xmax = 0.95, ymin = 0.55, ymax = 0.95),
                                     args = list(racecol = "lightgrey", end = c(0.8, 0.8))),
                                list(pos = list(xmin = 0.05, xmax = 0.45, ymin = 0.05, ymax = 0.45),
                                     args = list(racecol = "darkgreen", end = c(0.8, 0.9), width = 2)),
                                list(pos = list(xmin = 0.55, xmax = 0.95, ymin = 0.05, ymax = 0.45),
                                     args = list(racecol = "lightgrey", end = c(0.9, 0.85))))),
  ACRC = list(name = "Accept Complete Reject Complete",
              components = list(list(pos = list(xmin = 0.05, xmax = 0.45, ymin = 0.55, ymax = 0.95),
                                     args = list(racecol = "darkgreen", end = c(0.7, 0.95), width = 2)),
                                list(pos = list(xmin = 0.55, xmax = 0.95, ymin = 0.55, ymax = 0.95),
                                     args = list(racecol = "lightgrey", end = c(0.8, 0.8))),
                                list(pos = list(xmin = 0.05, xmax = 0.45, ymin = 0.05, ymax = 0.45),
                                     args = list(racecol = "darkgreen", end = c(0.7, 0.9), width = 2)),
                                list(pos = list(xmin = 0.55, xmax = 0.95, ymin = 0.05, ymax = 0.45),
                                     args = list(racecol = "darkred", end = c(0.55, 0.9), width = 2)))),
  Comp = list(name = "Compensatory",
              components = list(list(pos = list(xmin = 0.05, xmax = 0.45, ymin = 0.3, ymax = 0.7),
                                     args = list(racecol = "darkgreen", end = c(0.6, 0.9), width = 4)),
                                list(pos = list(xmin = 0.55, xmax = 0.95, ymin = 0.3, ymax = 0.7),
                                     args = list(racecol = "lightgrey", end = c(0.7, 0.8), width = 2))))
)


```


### All together

```{r}
p <- plot_canvas(xmax = 2, ymax = 3) +
  coord_fixed() +
  annotation_custom(ggplotGrob(arch_schema_plot('ASRS')),
                    xmin = 0.05, xmax = 0.95, ymin = 2.05, ymax = 2.95) +
  annotation_custom(ggplotGrob(arch_schema_plot('ASRC')),
                    xmin = 1.05, xmax = 1.95, ymin = 2.05, ymax = 2.95) +
  annotation_custom(ggplotGrob(arch_schema_plot('ACRS')),
                    xmin = 0.05, xmax = 0.95, ymin = 1.05, ymax = 1.95) +
  annotation_custom(ggplotGrob(arch_schema_plot('ACRC')),
                    xmin = 1.05, xmax = 1.95, ymin = 1.05, ymax = 1.95) +
  annotation_custom(ggplotGrob(arch_schema_plot('Comp')),
                    xmin = 0.55, xmax = 1.45, ymin = 0.05, ymax = .95)


print(p)

ggsave(
  filename = here::here(
    "results",
    "arch_mac_figures",
    "accumulators_diagram.png"),
  dpi = 600,
  width = 40,
  height = 60,
  units = "cm"
)
```
