---
title: "Figures for architecture_of_multiattribute_choice paper"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    theme: paper
    highlight: pygments
    df_print: kable
---


# Veridical Numeric Task

Before creating our plots we need to load in packages and prepare some convenience functions and themes for plotting.

## Load Packages

I use the tidyverse a lot, so we'll load that all in now, we also need the `BayesFactor` package, and `ggpubr` for combining subplots into larger figures. We'll also tell knitr to create all figures at the full column width.

```{r, message = FALSE}
library(dplyr)
#library(forcats)
library(ggplot2)
library(ggh4x)
library(stringr)
library(patchwork)
library(watercolours)
library(mcce)   # devtools::install_github('gjcooper/gcphd-model_of_dce')
knitr::opts_chunk$set(out.width = "100%")
```

## Load Data

```{r read_data}
# Load all the samples
accept_file <- here::here("data", "output", "NumericVDCE_1878182.rcgbcm_Estimation5Model.RData")
reject_file <- here::here("data", "output", "NumericVDCE_2117450.rcgbcm_RejectEstimation5Model.RData")

accept_samples <- get_samples(accept_file) %>% extract_parameters
reject_samples <- get_samples(reject_file) %>% extract_parameters

samples <- list(accept = accept_samples, reject = reject_samples) %>%
  bind_rows(.id = "condition")

#Map of old parameter names to new ones
par_labels <- c("ASRS", "ASRC", "ACRS", "ACRC", "Comp")
names(par_labels) <- c("FPP", "IST", "IEX", "MW", "CB")

```

## Plot theme

To keep things as consistent as possible we'll create a theme and update the default ggplot theme with it.

```{r}
txt_base_sz <- 12
plot_theme <- theme(
  strip.background = element_blank(),
  strip.text = element_text(face = "bold", size = txt_base_sz + 2),
  strip.placement = "outside",
  legend.title =  element_blank(),
  legend.position = "bottom",
  legend.margin = margin(0, 0, 0, 0, "cm"),
  axis.text = element_text(face = "bold", size = txt_base_sz - 2),
  axis.title = element_text(face = "bold", size = txt_base_sz + 2),
  plot.margin = margin(l = 2, r = 2, t = 2),
  plot.title = element_text(face = "bold", size = txt_base_sz + 2, hjust = 0.5),
)

bigger_text <- theme(
  axis.title = element_text(size = txt_base_sz + 4),
  strip.text = element_text(face = "bold", size = txt_base_sz + 4),
  plot.title = element_text(face = "bold", size = txt_base_sz + 4))


theme_set(theme_classic() + plot_theme)
```

## Selective Influence test

```{r}
model_medians <- samples %>%
  filter(startsWith(parameter, "alpha_"), stageid == "sample") %>%
  mutate(value = exp(value)) %>%
  group_by(subjectid, parameter) %>%
  summarise(value = median(value), condition = first(condition)) %>%
  arch_medians

Par_order <- c("IST", "CB", "FPP", "MW", "IEX")

acc_plot <- model_medians %>%
  filter(condition == "accept") %>%
  mutate(parameter = factor(parameter, levels = Par_order,
                            labels = par_labels[Par_order])) %>%
  arch_plot +
  scale_fill_watercolour(palette = "durer") +
  theme(legend.position = "none") +
  labs(title = "Accept condition")

rej_plot <- model_medians %>%
  filter(condition == "reject") %>%
  mutate(parameter = factor(parameter, levels = Par_order,
                            labels = par_labels[Par_order])) %>%
  arch_plot +
  scale_fill_watercolour(palette = "durer") +
  theme(legend.position = "right",
        legend.key.size = unit(2, "cm")) +
  labs(title = "Reject condition")

layout <- "
AAAAAAAAA
BBBB##CC#
"
acc_plot + rej_plot + guide_area() +
  plot_layout(design = layout, guides = "collect")

ggsave(
  filename = here::here(
    "results",
    "arch_mac_figures",
    "salience_manipulation.png"),
  dpi = 300,
  width = 45,
  height = 30,
  units = "cm"
)
```

## Parameter values for Veridical task

```{r}
par_medians <- samples %>%
  filter(!startsWith(parameter, "alpha_"), stageid == "sample") %>%
  mutate(value = exp(value)) %>%
  group_by(subjectid, parameter) %>%
  summarise(value = median(value), condition = first(condition))

par_colours <- c("t0" = "grey",
                 "A" = "grey", "b_acc" = "#73842E", "b_rej" = "#D0781C",
                 "v_acc_p_H" = "#569F72", "v_acc_p_L" = "#407755", "v_acc_p_D" = "#2B5039",
                 "v_rej_p_H" = "#F29F40", "v_rej_p_L" = "#EF8C1A", "v_rej_p_D" = "#BF6C0D",
                 "v_acc_r_H" = "#85C0FF", "v_acc_r_L" = "#47A0FF", "v_acc_r_D" = "#0A81FF",
                 "v_rej_r_H" = "#BBA9A0", "v_rej_r_L" = "#A2887C", "v_rej_r_D" = "#83685D")

par_medians %>%
  mutate(colour = par_colours[parameter]) %>%
  ggplot(aes(x = parameter, y = value, fill = colour)) +
  scale_colour_watercolour(palette = "durer") +
  scale_fill_identity() +
  geom_boxplot() +
  coord_flip() +
  facet_wrap(~ condition)

ggsave(
  filename = here::here(
    "results",
    "arch_mac_figures",
    "vnumeric_pars.png"),
  dpi = 300,
  width = 45,
  height = 30,
  units = "cm"
)
```

# Simulation

## Prep for data reads and get original data

```{r}
# Load all the samples
data_location <- here::here("data", "output", "VeridicalRecovery")
odata <- "NumericVDCE_1878182.rcgbcm_Estimation5Model.RData"

recovery_files <- list.files(data_location, pattern = ".RData")
recovery_data_files <- list.files(data_location, pattern = ".RDS")

original_samples <- get_samples(here::here("data", "output", odata))
```

## Read in generated data

```{r}
recovery_data <- lapply(recovery_data_files, function(x) {
  print(paste("Reading data", x))
  readRDS(here::here(data_location, x))
})
names(recovery_data) <- sapply(strsplit(recovery_data_files, "_"), "[[", 2)

recovery_data[["Original"]] <- original_samples$data %>%
  mutate(generator = "participant")
recovery_data <- bind_rows(recovery_data, .id = "source")
```

## Data plots

### Plot 1

```{r}
recovery_data %>%
  filter(rt < 10) %>%
  mutate(accept = factor(accept, labels = c("Reject", "Accept"))) %>%
  ggplot(aes(x = source, y = rt, colour = generator)) +
  geom_boxplot() +
  facet_wrap(~ accept) +
  scale_colour_watercolour(palette = "durer")

```

### Plot 2

```{r}
recovery_data %>%
  filter(rt < 5) %>%
  mutate(simulated = ifelse(source == "Original", "No", "Yes")) %>%
  mutate(cell=paste0(price, rating)) %>%
  ggplot(aes(x = rt, colour = source, linetype=simulated)) +
  geom_density(linewidth=0.7) +
  scale_colour_watercolour(palette = "durer") +
  facet_wrap(~ cell)
```


## Read in the samples

```{r}
samples <- lapply(recovery_files, function(x) {
  print(paste("Extracting", x))
  get_samples(here::here(data_location, x)) %>%
    extract_parameters
})
names(samples) <- sapply(strsplit(recovery_files, "_"), "[[", 2)

samples[["Original"]] <- original_samples %>% extract_parameters

samples <- bind_rows(samples, .id = "source")
rm(original_samples)

```

## Get Architecture Medians

```{r}
model_medians <- samples %>%
  filter(startsWith(parameter, "alpha_"), stageid == "sample") %>%
  mutate(value = exp(value)) %>%
  group_by(source, subjectid, parameter) %>%
  summarise(value = median(value)) %>%
  arch_medians(grouping_vars = c("source", "subjectid"))
```

## Get subject order for plot

```{r}
subject_order <- model_medians %>%
  filter(subjectid != "Group") %>%
  group_by(subjectid, source) %>%
  summarise(maxRel = max(rel_val)) %>%
  group_by(subjectid) %>%
  summarise(meanMax = mean(maxRel)) %>%
  arrange(desc(meanMax)) %>%
  pull(subjectid)
```

## Get parameter order

```{r}
Par_order <- model_medians %>%
  filter(source == "Original") %>%
  group_by(parameter) %>%
  summarise(median_val = median(rel_val)) %>%
  arrange(median_val) %>%
  pull(parameter)
```

## Architecture recovery

```{r}
subject_recovery <- model_medians %>%
  filter(source != "Original") %>%
  filter(subjectid != "Group") %>%
  mutate(subjectid = factor(subjectid, subject_order)) %>%
  mutate(parameter = factor(parameter, Par_order,
                            labels = par_labels[Par_order])) %>%
  mutate(source = factor(source, Par_order,
                         labels = par_labels[Par_order])) %>%
  ggplot(aes(x = subjectid, y = rel_val, fill = parameter)) +
    geom_col() +
    labs(y = "Relative Evidence") +
    scale_fill_watercolour(palette = "durer") +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          strip.background = element_blank(),
          strip.text.y = element_blank()) +
    facet_grid(rows = vars(source)) +
    scale_y_continuous(labels = NULL, breaks = NULL) +
    ggtitle("Indidividual Subjects")

group_recovery <- model_medians %>%
  filter(source != "Original") %>%
  filter(subjectid == "Group") %>%
  mutate(subjectid = factor(subjectid, subject_order)) %>%
  mutate(parameter = factor(parameter, Par_order,
                            labels = par_labels[Par_order])) %>%
  mutate(source = factor(source, Par_order,
                         labels = par_labels[Par_order])) %>%
  ggplot(aes(x = subjectid, y = rel_val, fill = parameter)) +
    geom_col() +
    scale_fill_watercolour(palette = "durer") +
    theme(axis.title = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank()) +
    facet_grid(rows = vars(source)) +
    scale_y_continuous(labels = NULL, breaks = NULL) +
    ggtitle("Group Level")

subject_recovery + group_recovery +
  plot_layout(widths = c(6, 1), guides = "collect") +
  plot_annotation(
    title = "Relative Evidence for each of the 5 architectures",
    subtitle = "Each row corresponds to the generating architecture",
    caption = "The area of each stacked bar is the relative proportion of each of the five possible modelled architectures as their dirichlet process"
    )

ggsave(
  filename = here::here(
    "results",
    "arch_mac_figures",
    "simulation_recovery.png"),
  dpi = 300,
  width = 45,
  height = 30,
  units = "cm"
)
```

## Parameter Recovery

```{r}
par_medians <- samples %>%
  filter(!startsWith(parameter, "alpha_")) %>%
  group_by(source, subjectid, parameter) %>%
  summarise(value = median(value))

recovery <- par_medians %>% filter(source != "Original")
original <- par_medians %>% filter(source == "Original")

model_order <- c("CB", "FPP", "MW", "IST", "IEX", "Original")

combined <- recovery %>%
  left_join(original, by = c("parameter", "subjectid")) %>%
  select(-source.y) %>%
  rename(
    recovered_value = value.x,
    estimated_value = value.y,
    recovery_model = source.x
  ) %>%
  mutate(recovery_model = factor(recovery_model, levels = model_order[-6],
                                 labels = par_labels[model_order[-6]])) %>%
  mutate(subjectid = case_when(
    subjectid == "theta_mu" ~ "Group",
    TRUE ~ str_pad(subjectid, 2, pad = "0")
  ))

scatter_caption <- str_wrap(paste(
  "The data generating values are the medians of the posterior for the full",
  "model estimated with the dirichlet process. The generation process uses the",
  "random sample function from only one of the 5 models.",
  "The recovered values are again the medians of the posterior for the full",
  "model (again with the dirichlet process)."
), 100)

pt_col <- watercolour$durer$discrete["shadow"]

parplot <- function(subset) {
  subset %>%
  ggplot(aes(x = estimated_value, y = recovered_value)) +
  geom_point(size = 0.5, colour = pt_col) +
  geom_abline(intercept = 0, slope = 1) +
  facet_grid2(rows = vars(parameter),
              cols = vars(recovery_model),
              scales = "free",
              independent = "x") +
  labs(
    x = "Generating Value",
    y = "Recovered Value",
    caption = scatter_caption
  )
}

combined %>%
  filter(parameter %in% c("A", "t0", "b_acc", "b_rej")) %>%
  parplot()

ggsave(
  filename = here::here(
    "results",
    "arch_mac_figures",
    "parameter_recovery_other.png"),
  dpi = 300,
  width = 45,
  height = 30,
  units = "cm"
)

```

### Accept drift rates

```{r}
combined %>%
  filter(startsWith(parameter, "v_acc")) %>%
  parplot

ggsave(
  filename = here::here(
    "results",
    "arch_mac_figures",
    "parameter_recovery_drift_acc.png"),
  dpi = 300,
  width = 45,
  height = 30,
  units = "cm"
)
```

### Reject drift rates

```{r}
combined %>%
  filter(startsWith(parameter, "v_rej")) %>%
  parplot

ggsave(
  filename = here::here(
    "results",
    "arch_mac_figures",
    "parameter_recovery_drift_rej.png"),
  dpi = 300,
  width = 45,
  height = 30,
  units = "cm"
)
```

# Architecture Explainer

```{r}
model_order <- model_order[c(4, 2, 3, 5, 1)]

one_acc_plot <- function(col = "darkgreen", end = c(0.8, 0.8), width = 2) {
  ggplot(data.frame(x = seq(0, 1, 0.1), y = seq(0, 1, 0.1)),
         aes(x = x, y = y)) +
  geom_blank() +
  geom_hline(yintercept = 0.9, linetype = 2) +
  geom_segment(
    x = 0, y = 0,
    xend = end[1], yend = end[2],
    lineend = "round", # See available arrow types in example above
    linejoin = "mitre",
    linetype = 1,
    size = width,
    arrow = arrow(length = unit(0.3, "inches")),
    colour = col # Also accepts "red", "blue' etc
  ) +
  theme(
    axis.line = element_line(linewidth=2),
    axis.title = element_blank(),
    axis.text = element_blank()
  ) +
  scale_x_continuous(expand = c(0, 0), limits = c(0, 1)) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 1))
}
```

### All together

```{r}
layout <- "
##BB#####
AABB#DDEE
AACC#DDEE
##CC#####
#########
FFHH#JJ##
FFHH#JJLL
GGII#KKLL
GGII#KK##
#########
MMMM#NNNN
MMMM#NNNN
MMMM#NNNN
MMMM#NNNN
"

# IST
one_acc_plot(end = c(0.6, 0.9)) +
  one_acc_plot("darkred", end = c(0.95, 0.6)) +
  one_acc_plot("darkred", end = c(0.95, 0.8)) +
# FPP
  one_acc_plot(end = c(0.6, 0.9)) +
  one_acc_plot("darkred", end = c(0.95, 0.8)) +
# MW
  one_acc_plot(end = c(0.6, 0.9)) +
  one_acc_plot(end = c(0.8, 0.9)) +
  qne_acc_plot("darkred", end = c(0.95, 0.6)) +
  one_acc_plot("darkred", end = c(0.95, 0.8)) +
# IEX
  one_acc_plot(end = c(0.6, 0.9)) +
  one_acc_plot(end = c(0.8, 0.9)) +
  one_acc_plot("darkred", end = c(0.95, 0.6)) +
# CB
  one_acc_plot(end = c(0.7, 0.9), width = 4) +
  one_acc_plot("darkred", end = c(0.95, 0.6), width = 4) +
  plot_layout(design = layout)

ggsave(
  filename = here::here(
    "results",
    "arch_mac_figures",
    "accumulators_diagram.png"),
  dpi = 300,
  width = 40,
  height = 60,
  units = "cm"
)
```
